---
title: "Lab 00 - Hello IDS!"
author: "Edwin-Valentin Ivanescu"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Marcel", "Josh", "Kenny", 
           "Luke", "Edwin"),
  github_username = c("marcelm237", "edivan05", "JM-56", 
                      "kenny-webb", "deathbringer"), 
  colour = c("red", "blue", "orange", 
             "green", "red"),
  hobby = c("Cooking", "Card Tricks", "Football", 
            "Hill Walking", "Writing"),
  favourite_number = c(7, 5, 3, 6, 3)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


*Favourite colour on x axis, favourite number on y axis*

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Favourite Colour", 
          y = "Favourite Number ",
          title = "Graph to show Favourite Colour and Number")
```

*.*

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*If it included everyone on the course, it would be an extremely big bar graph. Instead, it could be better to show the amount of people who's favourite colour is X and favourite number is Y. This will help make it much more concise.*
